---
title: "Distributions"
author: "BPR"
date: '2022-05-16'
output: word_document
---

To insert a chunk: Ctrl+Alt+I

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

install.packages("tidyverse")   # Put tidyverse on our bookshelf
library(tidyverse)              # Pull the book over to our desk
```


# Normal Distributions

## Determining normality

### Method 1: Histogram
```{r}
hist(pull(read_csv("http://bit.ly/NDSData")))
```
Is this normal data?


```{r betterHist}
hist(pull(read_csv("http://bit.ly/NDSData")),   # Get the data
     main = "Possibly normal data",             # Graph title
     xlab = "Data",                             # label of x-axis
     xlim = c(6,12),                            # lower and upper x limits
     breaks = 20)                               # Number of bins
```


### Shapiro-Wilk test
```{r}
shapiro.test(pull(read_csv("http://bit.ly/NDSData")))
```
H0 - Not significantly difference from normal distribution

Problem: Absence of evidence is not evidence of absence

### Q-Q plot
My favorite flavor comes from the car package
```{r}
library(car)

qqPlot(pull(read_csv("http://bit.ly/NDSData")))
```




# Code Your Own

Are the datasets NDSData2 and NDSData3 normal? Why or why not?

http://bit.ly/














