---
title: "Monday Afternoon"
author: "BPR"
date: '2022-05-16'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)  # Just because it is helpful
library(car)                        # qqPlot()
library(tidyverse)                  # pull(), read_csv() and more!
```


# Power Laws - Part I
```{r}
pull(read_csv("http://bit.ly/NDSMoby")) -> 
  moby_vec

hist(moby_vec,
     breaks = 100)
```
Moral: Histograms and power laws don't always mix well!

Normal doesn't work!
```{r}
shapiro.test(moby_vec)
qqPlot(moby_vec)
```
Quick and dirty check for power law behavior in the data. (Don't tell Clauset et al. (2009) that I said this!)
```{r}
plot(x = 1:length(moby_vec),          # x-data
     y = moby_vec,
     log = "xy",                      # Take the logarithm of the data!
     main = "Word frequency vs. rank",
     xlab = "Rank",
     ylab = "word frequency")

```
Because this plot is a straight line, the data are fat-tailled (e.g., power law, lognormal, etc.).

Why do we care? Barabasi & Albert: Power law indicates self-organization.

# Bounded distributions

```{r}
hist(pull(read_csv("http://bit.ly/AnxHighShape")))
shapiro.test(pull(read_csv("http://bit.ly/AnxHighShape")))
```

```{r}
hist(pull(read_csv("http://bit.ly/AnxLowShape")))
```


# Inference
```{r}
wilcox.test(pull(read_csv("http://bit.ly/AnxLowShape")),
            pull(read_csv("http://bit.ly/AnxHighShape")))

read_csv("https://bit.ly/NDSData4") -> 
  anxiety_df
wilcox.text(Anxiety ~ as.factor(Group),
      data = anxiety_df)

library(lmPerm)

summary(aovp(Anxiety ~ as.factor(Group),
      data = anxiety_df))
```



## Code Your Own
```{r}

wilcox.test(CSE ~ GoodFit,
            data = read_csv("http://bit.ly/NDSData5"))
```


# Burstiness
```{r}
devtools::install_github("barneyricca/buRst")
library(buRst)
```


```{r}
event_burstiness(pull(read_csv("http://bit.ly/NDSSpeakers")),
                 min_iet = 1)
event_burstiness(pull(read_csv("http://bit.ly/NDSMacro1")), # Fiore et al.
                 min_iet = 2)
```


# Fractals

```{r}
read_csv("http://bit.ly/NDSSierpinski") ->
  sp

str(sp)          # Get the columns (i.e., structure)

plot(x = sp$Scale,       # Dollar sign: Get the column named...
     y = sp$Remaining,
     log = "xy")
```


```{r}
log(sp$Remaining) -> yl  # Log of Remaining into yl
log(sp$Scale) -> xl      # Log of scale into xl
summary(lm(yl ~ xl))
```














