---
title: "Tuesday Morning"
author: "BPR"
date: '2022-05-17'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)  # Just do this.

library(igraph)                     # Need a function from igraph
library(tidyverse)                  # read_csv(), pull(), etc.
```


# Fractal (fractional) dimension
```{r paperCrumple}
read_csv("http://bit.ly/NDSPaperCrumple") ->  # Data file
  paper_df                                    # Make a "data frame"
str(paper_df)                                 # Look at structure

```

```{r crumpleDimension}
summary(                            # Print out everything
  lm(log(Diameter_A) ~ log(Size),   # Linear model (regression)
     data = paper_df)               # Data
)
```

```{r paperPlot}
lm(log(Diameter_A) ~ log(Size),   # Linear model (regression)
     data = paper_df) ->
  paper_lm                        # Store the linear model
{
  plot(paper_df$Size, paper_df$Diameter_A, # Plot the data
       log = "xy")                         # "log-log" plot
  abline(paper_lm,                         # Add a line of the lm()
         col = "blue") 
}

```

The better approach
```{r}
log(paper_df$Diameter_A) -> A_lg
log(paper_df$Size) -> Size_lg
summary(lm(A_lg ~ Size_lg))
```


Moral: The log-log regression is biased (esp. in the intercept)

In this case, the geometric dimension is related to the crumpling dimension by inversion: 1/0.43 = 2.317508


But the question is important: What does this dimension mean? Is it just a latent construct or proxy or does it mean something real?


```{r AFAR}
pull(read_csv("http://bit.ly/NDSAFAR")) -> afar

table(afar)

```



# Power Laws of Categorical Data

Approach 1: Time series data often need some additional help in determining the appropriate time scale. Enter _orbital decomposition_ (Guastello).

```{r}
pull(read_csv("http://bit.ly/NDSAFAR")) ->
  afar

devtools::install_github("barneyricca/fitpoweRlaw")
library(fitpoweRlaw)
```

Now, do some orbital decomposition:
```{r}
orbde(afar)
```
Ht = "topological entropy"

Minimum Ht is the appropriate length (C).

Pragmatically, use C = 1 for starters:
```{r}
sort(table(afar))
```

Fit power law:
```{r}
fit_power_law(unname(table(afar)))
```
Kolmogorov-Smirnov statistic

Why not a good fit?
```{r}
barplot(sort(table(afar), decreasing = TRUE))

```

log-log fit:

```{r}
sort(unname(table(afar)), 
     decreasing = TRUE) -> a1 # Distribution, sorted
log(a1) -> a1                              # Change to log
1:length(a1) -> x1                         # Make the ranks
log(x1) -> x1                              # change to log
summary(lm(a1 ~ x1))
```

# Code Your Own
NDSMacro1 and NDSMacro2 - same small group, different days
NDSMacro3 and NDSMacro4 - same days as Macro1 & 2, respectively, but different small group.

http://bit.ly/
```{r}
pull(read_csv("http://bit.ly/NDSMacro1")) -> a1
pull(read_csv("http://bit.ly/NDSMacro2")) -> a2
pull(read_csv("http://bit.ly/NDSMacro3")) -> a3
pull(read_csv("http://bit.ly/NDSMacro4")) -> a4

```

